\href{http://www.sigcomm.org/content/ebook}{Recent Advances in Networking}

### 2014-01-13 Compiled/intro/intro.tex
fixed typo

This eBook is composed of nine chapters chosen after a highly selective review process by the editorial board. The selected chapters cover advanced networking topics and accompanying teaching material (slides and exercises). All the source code of the eBook and the teaching material are kept on a version controlled repository that will be accessible for the entire SIGCOMM community. We expect that releasing such high quality teaching material will be beneficial for a large number of students and professors. The teaching material will be updated on a regular basis to reflect new advances in our field. We will also be adding new chapters on more emerging topics in the future volumes.

We wish to thank all there authors for providing such high quality chapters. We are also grateful to the reviewers and the editorial board for spending many hours on each chapter to ensure a coherent level amongst all the chapters. We hope you enjoy reading this eBook and find it a useful resource.\\

>>>>

The first edition of this eBook is composed of nine chapters chosen after a highly selective review process by the editorial board. The selected chapters cover advanced networking topics and accompanying teaching material (slides and exercises). All the source code of the eBook and the teaching material are kept on a version controlled repository that will be accessible for the entire SIGCOMM community. We expect that releasing such high quality teaching material will be beneficial for a large number of students and professors. The teaching material will be updated on a regular basis to reflect new advances in our field. We will also be adding new chapters on more emerging topics in the future volumes.

We wish to thank all the authors for providing such high quality chapters. We are also grateful to the reviewers and the editorial board for spending many hours on each chapter to ensure a coherent level amongst all the chapters. We hope you enjoy reading this eBook and find it a useful resource.\\
